Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
an other -> another

\noindent A common expectation is, that a value should be equal to an other
value:

@@

\noindent This is just an other name for HUnit's \texttt{@?=}
operator.  The type is:

>>>>

\noindent A common expectation is, that a value should be equal to another
value:

@@

\noindent This is just another name for HUnit's \texttt{@?=}
operator.  The type is:
